The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-23 System/components.tex
fixed some small things Fixed all todos till sys design

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again).
The Fuzzer is the only component that interacts directly with the external web applications. The Fuzzer is split into smaller modules, each of which is responsible for a particular type of fuzzing.  The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability. Making HTTP requests is an expensive process~\cite{McGrath2009}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads used for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

@@

	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems. %Adam: have a citation for this?

@@

Along with the payload, the Fuzzer also injects data into the other fields of the form. This data must pass validation constraints on the individual input fields (e.g.,\ for a name field, numbers might not be allowed). To maximize the amount of vulnerabilities the system discovers, the data injected into the input fields should adhere to the constraints. The Fuzzer uses a ``Data Dictionary'' which has predefined ``keys'' and ``values'' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}.
% Adam: What does it mean here for these to be generated on-the-fly? Using templates?
The default values for these are generated on-the-fly for each form, based on generally followed guidelines for such fields. For example, password fields should consist of at least one uppercase letter, one lowercase letter, and a special character.
% Adam: can you add a sentence here about crawling and fuzzing fields on the web is an open problem (and cite ``Crawling the hidden web''

>>>>

\subsubsection{Fuzzer}
\label{Comp:Fuzzer}
% Adam: we should call these something else but modules. We already have the top two modules, which are composed of components, now we need to split these into something (not components again). - DONE
The Fuzzer is the only component that interacts directly with the external web applications. The Fuzzer is split into smaller parts, each of which is responsible for a particular type of fuzzing.  The system injects payloads in two stages: the goal is to reduce the total number of HTTP requests the system generates to detect an \ehi vulnerability. Making HTTP requests is an expensive process~\cite{McGrath2009}, and can cause bottlenecks in a Crawler-Fuzzer system~\cite{ShkapenyukTorstenSuel2001}.
The two different types of payloads used for fuzzing are:
\paragraph{Non-Malicious Payload}
\label{Comp:Fuzzer:nmp}
The regular or non-malicious payload is simply an \email address. The goal is to see if the web application will send an \email message based on our input. The specific format of the \email is \texttt{reguser(xxxx)@example.com}, where \texttt{xxxx} is replaced by an internal id that uniquely maps the payload to the form, and \texttt{example.com} is replaced by our domain.

@@

	This payload is added for purposes of cross-platform fuzzing: \texttt{\textbackslash{}r\textbackslash{}n} is the ``Carriage Return - New Line (CRLF)'' used on Windows systems.~\cite{rfc2616}

@@

Along with the payload, the Fuzzer also injects data into the other fields of the form. This data must pass validation constraints on the individual input fields (e.g.,\ for a name field, numbers might not be allowed).  As crawling and fuzzing input fields on the web is an open problem~\cite{raghavan2000crawling}, we chose to go with a best-effort approach. To maximize the amount of vulnerabilities the system discovers, the data injected into the input fields should adhere to the constraints. The Fuzzer uses a ``Data Dictionary'' which has predefined ``keys'' and ``values'' for standard input fields such as \texttt{name}, \texttt{date}, \texttt{username}, \texttt{password}, \texttt{text}, and \texttt{submit}.
% Adam: What does it mean here for these to be generated on-the-fly? Using templates? - Fixed.
The default values for these are generated from the Data dictionary for each form, based on generally followed guidelines for such fields. For example, password fields should consist of at least one uppercase letter, one lowercase letter, and a special character.
% Adam: can you add a sentence here about crawling and fuzzing fields on the web is an open problem (and cite ``Crawling the hidden web'' - DONE.
